|

### 2021-08-11 prova_knit_finale.Rmd
changes on chunks

First, a general point is that the sequence of percentage log returns are different across the three indices. The reasons why this holds can be associated with the index-construction method and the characteristics of the economy and industrial setting it represents. In particular, as previously noticed, there are extensive similarities between the DOW JONES Index and the S&P500, which can be visualized when looking at the percentage of log returns in the corresponding plots, since both are describing the US Economy. However, the STOXX50E differs quite extensively, especially in the different sensitivity to the Covid-19 Crisis and its consequences,  representing the European Economy. Aside from this note, the considerations expressed below on the sequences "filtered volatilities" for the various techniques hold almost uniformly for all the three indices. Therefore, in the next paragraph we will be referring to the set of plots pertaining to one specific index (which could be any of the three).\

@@

@@

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
      weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x)^2)-((data[t]^2)/2)*exp(-alpha-beta*x)*(1+alpha+beta*x))
      k   = sample(1:N,size=N,replace=TRUE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   = rep(1/N,N)
    }else{
      weight = rep(1/N,N)
      k   = sample(1:N,size=N,replace=FALSE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   <-  w*dnorm(data[t],0,exp(x1/2))*dnorm(x1,alpha+beta*x[k],tau)/
        dnorm(x1,mean=alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    }

>>>>

First, a general point is that the sequences of percentage log returns are different across the three indices. The reasons why this holds can be associated with the index-construction method and the characteristics of the economy and industrial setting it represents. In particular, as previously noticed, there are extensive similarities between the DOW JONES Index and the S&P500, which can be visualized when looking at the percentage of log returns in the corresponding plots, since both are describing the US Economy. However, the STOXX50E differs quite extensively, especially in the different sensitivity to the Covid-19 Crisis and its consequences,  representing the European Economy. Aside from this note, the considerations expressed below on the sequences "filtered volatilities" for the various techniques hold almost uniformly for all the three indices. Therefore, in the next paragraph we will be referring to the set of plots pertaining to one specific index (which could be any of the three).\

@@

    xprev<-x
    x<-rnorm(N,alpha+beta*x+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x))-2),tau)
    w1<-w*dnorm(data[t],0,exp(x/2))* dnorm(x,alpha+beta*xprev,tau)/dnorm(x,mean=alpha+beta*xprev+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*xprev))-2),tau)

@@

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
      weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x)^2)-((data[t]^2)/2)*
      exp(-alpha-beta*x)*(1+alpha+beta*x))
      k   = sample(1:N,size=N,replace=TRUE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   = rep(1/N,N)
    }else{
      weight = rep(1/N,N)
      k   = sample(1:N,size=N,replace=FALSE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   <-  w*dnorm(data[t],0,exp(x1/2))*dnorm(x1,alpha+beta*x[k],tau)/
        dnorm(x1,mean=alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    }
